%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,merriweather]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\rmdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.89]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
% \setlength{\makecvtitlenamewidth}{100cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Zhouxiao}{Wu}
\address{3113 Evergreen Drive}{Wilmington, MA 01887}{}
\phone[mobile]{+1~(617)~775~2961}                   % optional, remove / comment the line if not wanted
\email{wuzhouxiao@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{wtfruby.com}                         % optional, remove / comment the line if not wanted
%----------------------------------------------------------------------------------------
%  RESUME
%----------------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace{-1.5cm}

%----------------------------------------------------------------------------------------
%  EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry
{Feb 2016 - present}
{Ora Inc.}{Software Developer}{Andover, MA}{}
{Being a leading software developer in R\&D, provide company and clients with sophisticated tools for clinical trials and data analysis.
\begin{itemize}
\item Developed Android apps that collects data from thousands of subjects in real time as well as for post data analysis using firebase
\item Applied machine learning with opencv to do signal processing from Bluetooth wearable devices
\item Deployed Dlib and Opencv with HD cameras, leverage sympton collections from subjects
\item Improved user friendliness by understanding that users were not familiar with new technology to speed up clinical trials
\end{itemize}}
\vspace{.05cm}

\cventry
{Aug 2014 - Dec 2015}
{WPI and Umass Medical School}{Android App Developer, Research Assistant}{Worcester, MA}{}
{Being in a research team, developed an Android app which helps users to monitor and reduce their stress levels, as well as provides basic functionalities like logging food consumptions and daily activities, managing and visualizing data, etc. 
\begin{itemize}
\item Participated full development life cycle, joined focus groups to learn what potential users' needs
\item Devised RESTful services performed code reviews for peers
\end{itemize}}
%\vspace{.05cm}

%----------------------------------------------------------------------------------------
%  Projects SECTION
%----------------------------------------------------------------------------------------
\section{Projects}

\cventry
{Dec 2016 - Sep 2017}
{Ora Inc.}{Blink Detection with Camera}{Andover, MA}{}
{As the leading programmer in a research team, with improved Dlib's face landmarks detection and optimized OpenCV implementation, developed and implemented an application that accurately detects user's blink patterns and provides real-time data analysis for various ophthalmology research purposes.}
\vspace{.05cm}

\cventry
{Mar 2016 - Mar 2017}
{Ora Inc.}{Blink Detection with Wearable EEG Device}{Andover, MA}{}
{Being a solo programmer, developed both the Android app that connects to a wearable EEG device via Bluetooth and an efficient algorithm that filters out blinks from the EEG signals in real time and detects user's movement using signals from accelerometers in the EEG device.}
\vspace{.05cm}

\cventry
{Jan 2017 - Present}
{Ora Inc.}{Webiste for Site Payment Management using Firebase}{Andover, MA}{}
{Full stack web development using Firebase, implement a fully interactive web application for project managers to managnemt clinical trails and payments.   }
\vspace{.05cm}

\cventry
{Feb 2016 - May 2016}
{Ora Inc.}{Thermal Image Processing Project}{Andover, MA}{}
{Led a two-member team developing a Windows application in C++ using OpenCV to track eyes in thermal videos shot by an FILR camera to extract temperature data from specific areas of an eye. }
\vspace{.05cm}

\cventry
{Mar 2015 - May 2015}
{WPI}{Android Mobile App Class Project}{Worcester, MA}{}
{Led a three-member team in developing an Android app named "Foodrack" which allows users to order foods from restaurants on campus using Android Studio. Practiced OO design and the Agile development with Git and Github for version control. Used Google Location API, Twilio, Braintree, Firebase and Parse for backend and other features like tracking order's status and location in real time. }
%\vspace{.05cm}

%----------------------------------------------------------------------------------------
%  SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
\cvitem{Language}{Java, C++, Python, JavaScript, Objective-C, HTML5, CSS, C}
\cvitem{Software}{Android Studio, Android NDK, Eclipse, Visual Studio}
\cvitem{Technology}{Git, OpenCV, Dlib, Tensorflow, Machine Learning, Node.js, Firebase, REST, JSON, SQLite, Heroku}


%----------------------------------------------------------------------------------------
%  Visa SECTION
%----------------------------------------------------------------------------------------

\section{Visa and Sponsorship}
\cventry{}{Currently holding a H1B visa, can start work right after filing H1B transfer}{H1B Visa Holder}{}{}{}  % arguments 3 to 6 can be left empty

%----------------------------------------------------------------------------------------
%  EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2011--2015}{B.S Computer Science \textbf{3.5}/4.0}{Worcester Polytechnic Institute}{Worcester, MA}{}{}  % arguments 3 to 6 can be left empty

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{Publications}
\small Zhouxiao Wu; Endri Angjeli; John D. Rodriguez; George W. Ousler; Keith J. Lane1; David A. Hollander: \textbf{Effect of Activity on Interblink Interval Assessed with Continual Blink Tracking using the iBlink® in Normal Subjects}, \textit{ARVO 2017}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}

\clearpage

%----------------------------------------------------------------------------------------
%  COVER LETTER
%----------------------------------------------------------------------------------------

% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Sincerely,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle

%Test

%\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
